Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-26 paper/tex/sections/variations.tex
add in the new variation figures

\subsection{Properties of detectable systems}\label{sec:property_variations}
\tom{This will be about how the shapes of the parameter distributions change for the different model variations. I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}

>>>>

\subsection{Properties of detectable systems}\label{sec:property_variations}
\todo{Describe the plots -- also explore whether there is anything interesting the CE ones once they are done}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{lower_mass_gap_rapid_variation.pdf}
    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions. Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}}
    \label{fig:lower_mass_gap_variation}
\end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{ecc_low_kick_variation.pdf}
    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model as dashed lines.}
    \label{fig:ecc_low_kick_variation}
\end{figure}

% \begin{table}[htb]
%     \centering
%     \begin{tabular}{l|cccc}
%         \hline
%         \multirow{2}{*}{Component} & At Formation & \multicolumn{3}{c}{LISA detectable (4 year)} \\ \cline{2-5}
%         & All & BHBH & BHNS & NSNS \\
%         \hline
%         Low-$\alpha$ disc & 42.5\% & 88.6\% & 81.8\% & 84.9\%\\
%         High-$\alpha$ disc & 42.5\% & 5.2\% & 8.1\% & 12.0\%\\
%         Bulge & 15.0\% & 6.2\% & 10.1\% & 3.1\%\\
%     \end{tabular}
%     \caption{Percentage of systems in each Galactic component.}
% \end{table}
